Efficient GPU implementation of multicomponent and multiphase Lattice Boltzmann models.

### 2010-05-25 sources/twophase_poiseuille.tex
Fix sings in the 2phase Poiseuille derivation.

We are solving the Navier-Stokes equations in the 2D Cartesian coordinate system, assuming the system is driven by an
external acceleration field $g$ (in the Y direction):
\begin{align}
	\rho_i \left( \frac{\partial v_{ix}}{\partial t} + v_{ix} \frac{\partial v_{ix}}{\partial x} + v_{iy} \frac{\partial v_{ix}}{\partial y} \right) &= \mu_i
		\left( \frac{\partial^2 v_{ix}}{\partial x ^2 } + \frac{\partial^2 v_{ix}}{\partial y^2} \right) \\
	\rho_i \left( \frac{\partial v_{iy}}{\partial t} + v_{ix} \frac{\partial v_{iy}}{\partial x} + v_{iy} \frac{\partial v_{iy}}{\partial y} \right) &= \mu_i
		\left( \frac{\partial^2 v_{iy}}{\partial x ^2 } + \frac{\partial^2 v_{iy}}{\partial y^2} \right) + g \rho_i
\end{align}
We assume the flow to be stationary, so the time derivatives are 0.  We also take $v_{ix} = 0$, so the first equation
does not give us any further information about the system, while the second equation reduces to:
\begin{equation}
	- \frac{g \rho_i}{\mu_i} = \frac{\partial^2 v_{iy}}{\partial x^2}
\end{equation}
if we also asuume $\partial v / \partial y = 0$ (the flow is fully developed).  The general solution is:
\begin{equation}
	v_{iy} = \frac{g \rho_i}{2 \mu_i} x^2 + C_i x + D_i
	\label{eq:gensol}
\end{equation}
If we assume the phase interface to be located at $x = 0$, the continuity of $v$ requires $D_1 = D_2 = D$ and continuity of $\mu_i \partial_x v_i$ requires $\mu_1 C_1 = \mu_2 C_2$.

>>>>

We are solving the Navier-Stokes equations in the 2D Cartesian coordinate system, assuming the system is driven by an
external acceleration field $-g$ (in the Y direction):
\begin{align}
	\rho_i \left( \frac{\partial v_{ix}}{\partial t} + v_{ix} \frac{\partial v_{ix}}{\partial x} + v_{iy} \frac{\partial v_{ix}}{\partial y} \right) &= \mu_i
		\left( \frac{\partial^2 v_{ix}}{\partial x ^2 } + \frac{\partial^2 v_{ix}}{\partial y^2} \right) \\
	\rho_i \left( \frac{\partial v_{iy}}{\partial t} + v_{ix} \frac{\partial v_{iy}}{\partial x} + v_{iy} \frac{\partial v_{iy}}{\partial y} \right) &= \mu_i
		\left( \frac{\partial^2 v_{iy}}{\partial x ^2 } + \frac{\partial^2 v_{iy}}{\partial y^2} \right) - g \rho_i
\end{align}
We assume the flow to be stationary, so the time derivatives are 0.  We also take $v_{ix} = 0$, so the first equation
does not give us any further information about the system, while the second equation reduces to:
\begin{equation}
	\frac{g \rho_i}{\mu_i} = \frac{\partial^2 v_{iy}}{\partial x^2}
\end{equation}
if we also asuume $\partial v / \partial y = 0$ (the flow is fully developed).  The general solution is:
\begin{equation}
	v_{iy} = \frac{g \rho_i}{2 \mu_i} x^2 + C_i x + D_i
	\label{eq:gensol}
\end{equation}
If we assume the phase interface to be located at $x = 0$, the continuity of $v$ requires $D_1 = D_2 = D$ and continuity of $\mu_i \partial_x v_i$ requires $\mu_1 C_1 = \mu_2 C_2$.
